---
output:
  pdf_document: default
  html_document: default
---

# Dummy Records

This is a collation of all Dummy records from the **\_records** directory which comprises the source documents for all the ID sheets.


```{r  include=TRUE, echo=FALSE,  message=FALSE, results = 'asis'}

# This code collects all the markdown records from the _records directory and
# assembles a chapter from them.
#recordID <- "202011051101PJP"

# Make sure that these library files are available
library(plyr)
library(tidyverse)
# Read all rds files
absolutePath <- getwd()
path.to.all.data <- fs::path(absolutePath,"_records")

my.record.files <- list.files(
  path.to.all.data,
  pattern = ".Rmd", # Make a suitable filter. Use the dot for a wildcard.
  full.names = TRUE,
  recursive = TRUE) 

# This drops all files that begin with an underscore.
my.record.files.rows <- grep('^_', fs::path_file(my.record.files), invert = TRUE )

my.record.files <- my.record.files[my.record.files.rows]
# Absolute path needed as a workaround to make this work with child files
# absolutePath <- getwd()
# full.path <- fs::path(absolutePath,"_records" , recordID, recordID, ext = "Rmd")
# 
# path_to_pro_forma <- full.path
my.output <- NULL
my.count.identified <- 0
my.records.to.do <- NULL
my.records.prepared <- NULL
my.records.noid <- NULL
if( length(my.record.files) > 0) { # Check we have some records to include.
  # If we have records then included them
  for(my.record in my.record.files) {
    # Dummy values to cover no rds file.
    my.record.taxon <- 1
    my.record.order <- 1
    # Check to see if we have an .rds store
    my.record.rds <-  fs::path_ext_set(my.record, "rds" ) 
    my.record.rds.exists <- my.record.rds %>% fs::file_exists()
      if(my.record.rds.exists) {
       my.record.name <- fs::path_file(my.record) %>% fs::path_ext_remove() 
      my.record.data <- readRDS(my.record.rds)  
      # Which row has taxon
      my.record.taxon <- which(my.record.data$datumAttribute == "taxon")
      my.record.order <- which(my.record.data$datumAttribute == "order")
      } # We now know if the record has been identified
    
    # Save some space on checking order
    if(my.record.rds.exists) {
    is.this.my.order <- my.record.data$datumValue[my.record.order]   == "Dummy"
    }else{
    # Compile the record to update it but do not use it.
    temp.record. <- knitr::knit_child(my.record, quiet = TRUE)
      is.this.my.order <- FALSE }    
    # Save some space on checking order
    is.this.my.order <- my.record.data$datumValue[my.record.order]   == "Dummy"
  
  # Now we use an if ladder to apply actions to the record      
  if ( (my.record.data$datumValue[my.record.taxon]   == "Taxon") &
       (is.this.my.order)
       
       ){
    
    # Keep a tally of records to identify.
    # get the file name from the path
    
    my.records.to.do <- c(my.records.to.do, my.record.name )
    my.records.to.do <- sort(my.records.to.do)
    
    # Compile the record to update it but do not use it.
    temp.record. <- knitr::knit_child(my.record, quiet = TRUE)
    
  } else if (my.record.data$datumValue[my.record.taxon]   == "Prepared" &
       (is.this.my.order)){
    
    my.records.prepared <- c(my.records.prepared, my.record.name )
    my.records.prepared <- sort(my.records.prepared)
    # Compile the record to update it but do not use it.
    temp.record. <- knitr::knit_child(my.record, quiet = TRUE)    
    
  } else if (my.record.data$datumValue[my.record.taxon]   == "NoID"&
       (is.this.my.order)){
    
    my.records.noid <- c(my.records.noid, my.record.name )
    my.records.noid <- sort(my.records.noid)
    # Compile the record to update it but do not use it.
    temp.record. <- knitr::knit_child(my.record, quiet = TRUE)    

    
  } else if (my.record.data$datumValue[my.record.order]   == "Dummy")  {
    # We assume that the record has been identified.
    my.count.identified <- my.count.identified + 1
    # Compile the record and use it
    my.output <- c(my.output, knitr::knit_child(my.record, quiet = TRUE)) 
  }

  # cat('\\newpage')
  # cat(res, sep = '\n') 
  
  } # End for loop



} # End if records to include

  # cat('\\newpage')
  # cat(my.output, sep = '\n')



```



```{r eval = TRUE, include=TRUE, echo=FALSE,  message=FALSE, results = 'asis'}
# This creates a readme file in the _records repository and a Status chapter in
# the report. Building the book three times may be needed to update the figures.
absolutePath <- getwd()
path.to.all.data <- fs::path(absolutePath,"_records")
path.to.readme.template <- fs::path(path.to.all.data,"_template_readme",ext = "Rmd")

# Get the data-ss.rds for statistics. This may be out of step so need to allow
# for its absence.
path.to.data.ss <- fs::path(absolutePath,"data-ss","data-ss", ext = "rds")
if (fs::file_exists(path.to.data.ss)) {
  my.data.ss <- readRDS(path.to.data.ss)
    my.data.ss.rows.to.keep <- which(my.data.ss$order == "Dummy")
    my.data.ss.order <- my.data.ss[my.data.ss.rows.to.keep,]
    number.of.records.in.this.order <- nrow(my.data.ss.order)
} else {
  # This sort of makes sense in context.
  number.of.records.in.this.order <- "some"
}

    
    
my.template <- readr::read_file(path.to.readme.template) %>% as.character()
   # Rewriting to use whisker template
   my.lists <- list(
     my.orders = "Dummy",
     my.record.files.total = number.of.records.in.this.order,
     my.count.identified = my.count.identified,
     length.my.records.noid = length(my.records.noid),
     combine_words.my.records.noid = knitr::combine_words(my.records.noid),
     length.my.records.prepared = length(my.records.prepared),
     combine_words.my.records.prepared = knitr::combine_words(my.records.prepared),
     length.my.records.to.do = length(my.records.to.do),
     combine_words.my.records.to.do = knitr::combine_words(my.records.to.do )
     
     )

   mylists <- as.list(my.lists)
  my.rendered.output <- whisker::whisker.render(my.template, data = my.lists, strict= FALSE)
   #m Create a readme in the _records directory.
  
  
  rendered.path <- fs::path(path.to.all.data,"_README-Dummy", ext = "md")
  
  # The readme file does not need {-} tags
  rendered.readme <- gsub("\\{-\\}", "", my.rendered.output )
  
  readr::write_file(rendered.readme, rendered.path)
  
  
  # Use the same template to create status chapters

# Remove status chapter as we just keep the md readme.  
  #   rendered.path <- fs::path(absolutePath,"04-status-Dummy", ext = "Rmd")
  # readr::write_file(my.rendered.output, rendered.path)
  # 
  
```

`r paste(my.output, collapse = "\n")`

<!--chapter:end:03-Dummy-records.Rmd-->



```{r}
library(plyr)
library(tidyverse)
library(ggplot2)
library(viridis)


absolute.path <- rprojroot::find_rstudio_root_file()
#CountyBoundary <- External[[2]]
path.to.VC55 <- fs::path(absolute.path, "data-ext","VC55", ext = "rds")

CountyBoundary <- readRDS(path.to.VC55)
# Set the ESPG
#CountyBoundary <- sf::st_set_crs(CountyBoundary, 4326)
# Reproject
# Reproject as UKNG EPSG 
CountyBoundary <- sf::st_transform(CountyBoundary, 27700)


```



```{r  fig.align='center', fig.cap= 'Map of all records by tetrad.' }

# Load the data
path.to.my.data <- fs::path( absolute.path
                               ,"data-ss","data-ss", ext = "rds")

my.data.ss <- readRDS(path.to.my.data)


# Rough check for sensible Grid reference format
data.for.spatial <- my.data.ss$grid.ref

      rows.with.GR <- grepl("([A-Z]{2})(\\d{4}|\\d{6}|\\d{8}|\\d{10})$",data.for.spatial )

   rows.to.keep <- which(rows.with.GR)  

   my.data.ss <-my.data.ss[rows.to.keep,]
   
   

my.data.geo <- eco.atlas::GBNG.to.Lat.Long(my.data.ss$grid.ref)

my.dates <- eco.atlas::Clean.dates(my.data.ss$record.date)

working.data <- cbind(my.data.ss, my.dates, my.data.geo )

all.data.df.sf <- sf::st_as_sf(working.data, coords= c("Long","Lat"))

# Set EPSG 4326 WSG84 as this is the source data
all.data.df.sf <- sf::st_set_crs(all.data.df.sf, 4326)

# Reproject as UKNG EPSG 
all.data.df.sf <- sf::st_transform(all.data.df.sf, 27700)

# Now we have data as UKNG we can work out tetrads

coordinates.of.records <- sf::st_coordinates(all.data.df.sf)

coordinates.of.records.2k <- trunc(coordinates.of.records/ 2000) *2000
colnames(coordinates.of.records.2k) <- c("X.2k", "Y.2k")
all.data.df.sf <- cbind(all.data.df.sf, coordinates.of.records.2k)
# Add coordinates as eastings and northings
coords.east.north <- coordinates.of.records
colnames(coords.east.north) <- c("easting", "northing")
all.data.df.sf <- cbind(all.data.df.sf, coords.east.north)

# Crop data

working.data <- sf::st_crop(all.data.df.sf, CountyBoundary)


#working.data <- all.data.df.sf
gplot1 <- ggplot()  + 
 geom_sf(data =CountyBoundary ) +
  geom_bin2d( data = working.data, 
              binwidth = c(2000,2000), 
              aes(x=easting, y=northing)) + 
              coord_sf(crs = 27700) +  
              scale_fill_viridis(trans = "log10")

gplot1

```


```{r  include=TRUE, fig.align='center', fig.cap= 'Phenology of all records.'}

# Create factor of included years
YYYY.factor <- working.data$YYYY %>% unique() %>% as.character() %>% fct_inseq()
MM.factor <- c("01","02","03","04","05","06","07","08","09","10","11","12")

working.data$count <- 1
temp.data.ag.by.month = aggregate(count ~ YYYY + MM, 
                                         data=working.data, sum, na.rm=TRUE)
# Add missing factor levels

temp.data.ag.by.month$YYYY <- factor(temp.data.ag.by.month$YYYY, YYYY.factor) %>% fct_inseq()
# Addd missing factor values
temp.data.ag.by.month$MM <- factor(temp.data.ag.by.month$MM, 
  levels = MM.factor )

# temp.data.ag.by.month.all$MM <- temp.data.ag.by.month.all$MM %>% as.numeric()
# temp.data.ag.by.month.all <- temp.data.ag.by.month.all[order(temp.data.ag.by.month.all$MM),]


gplotStrip <- ggplot(data = temp.data.ag.by.month)  +
    ggtitle("Records by month") +
  geom_tile( 
                      aes(x=YYYY,y=MM, fill= count))  +
   scale_y_discrete(drop = FALSE) + 
  scale_x_discrete(drop = FALSE) + 
  scale_fill_viridis( discrete = FALSE, trans = "log10", option = "A") + 
  theme_minimal() +  coord_fixed() +
  theme(axis.text.x  = element_text(angle=45, hjust = 1),
        axis.title = element_blank())

#grid.arrange(gplot1, gplot3, nrow = 1)

#grid.arrange(gplot1, gplotpost, gplotStrip, nrow = 2)
lay <- rbind(c(1,2),
             c(3,3))

#grid.arrange(gplot1,  gplotStrip, layout_matrix = lay)

gplotStrip

```


<!--chapter:end:07-map.Rmd-->

---
title: Report On Identification Of VC55 Lepidoptera By Dissection
authors:
  - name: Dr Paul J. Palmer
    thanks: Thanks for everyone who helped.
    department: Author and Determination
    affiliation: Microscope ID Club
    location: Leicestershire VC55
    email: palmerpjp@gmail.com
  - name: Pete M. Leonard
    department: Author and Determination
    affiliation: Microscope ID Club  
    location: Leicestershire VC55
    email: peteleonard72@gmail.com    
abstract: |
  This report records the determinations made by microscopic examination of Lepidoptera specimens made by VC55 recorders. Each determination is illustrated by micro-photographs of specimens and temporary slides. 
bibliography: references.bib
biblio-style: unsrt
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    extra_dependencies: ["flafter"]
    includes:
      in_header: "preamble.tex"  

---

# Introduction

This report records the determinations made by microscopic examination of Lepidoptera specimens made by VC55 recorders. Specimens were not retained, as each determination is illustrated by micro-photographs of specimens and temporary slides. The high quality micro-photographs were produced by stacked focus photography and are much easier to work with than traditional permanent slides. In most cases, the artificial depth of field provides a better view of dissected parts than can be seen through a microscope. Using micro-photographs has also allowed on-line collaboration using the version management tool GitHub (https://github.com) to manage this and other reports. 

The primary sources for identifying Lepidoptera by dissection used in this work are @Hall2021 and @Schon2021. The determination was also checked against the appearance of the imago using @Kimber2021 amongst other sources.


# Species Summary

The species recorded are presented in Table \@ref(tab:TableSpeciesList) which has been directly generated from the records.

```{r TableSpeciesList, include=TRUE, echo=FALSE, message=FALSE}

library(plyr)
library(tidyverse)
library(kableExtra)
library(gridExtra)

absolute.path <- rprojroot::find_rstudio_root_file()

path.to.my.data <- fs::path( absolute.path
                               ,"data-ss","data-ss", ext = "rds")

my.data.ss <- readRDS(path.to.my.data)

columns.to.keep <- c("order","family","taxon","gender")

my.species.present <- my.data.ss[,columns.to.keep]

my.species.present$gender <- my.species.present$gender %>% unlist()

#my.species.present$num <- 1
my.species.present.gender <- pivot_wider(data = my.species.present, names_from =  gender)

my.species.summary <-   my.species.present %>% group_by(family, taxon, gender) %>% 
  tally(name = "Count") %>% arrange(family,taxon)

# Drop rows where family = Family
rows.to.keep <- !grepl("Family",my.species.summary$family )
my.species.summary.clean <- my.species.summary[rows.to.keep,]

knitr::kable(my.species.summary.clean, caption = 'Species recorded by family and gender.',booktabs = TRUE) %>%   kable_styling(latex_options = "striped")

rows.to.keep <- !grepl("Unknown",my.species.summary$family )
my.species.summary.ID <- my.species.summary[rows.to.keep,]
```

A total of `r sum(my.species.summary.ID$Count)` specimens were examined of which `r sum(my.species.summary.clean$Count)` were identified.


```{r, child= c('_working_code_blocks.Rmd','07-map.Rmd', '03-Dummy-records.Rmd' )}

```


# References {-}
<div id="refs"></div>
\let\cleardoublepage\clearpage

<!--chapter:end:dissection-report.Rmd-->

