
\documentclass{article}
\usepackage[a-1b]{pdfx}
\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage[style=british]{csquotes}
\hypersetup{hidelinks}
\title{\myTitleMainTitle}

\author{
    Dr Paul J. Palmer
    \thanks{Written to fulfil an action of the LES AGM.}
   \\
    Leicestershire Entomological Society \\
  \texttt{\href{mailto:palmerpjp@gmail.com}{\nolinkurl{palmerpjp@gmail.com}}} 
} 



% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%\usepackage{booktabs}
%\usepackage{longtable}
%\usepackage{morefloats}
%\extrafloats{100}
%\date{August 25, 2021}
%\renewcommand{\today}{September 5, 2021}

% Set the copyright footer
%\lfoot{\copyright 2021 P.J. Palmer  P.M. Leonard}

% Some figure placement options.
%\usepackage[figuresonly,nomarkers,fighead, figlist]{endfloat}
%\usepackage[figuresonly,nomarkers,nolists]{endfloat}
% Put multiple figures per page
%\renewcommand{\efloatseparator}{\mbox{}}
\usepackage{flafter}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\begin{document}
\maketitle


\begin{abstract}
\myAbstract
\end{abstract}


\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Electronic publication offers opportunities for producing of authoritative reports with citable references other than with the ISBN associated with traditional publication through printed documents. The use of a DOI (Digital Object Identifier) is well known in the academic community, as a means to permanently reference online versions of published papers in addition to the ISBN or ISSN associated with the printed journal or conference proceedings. However, a DOI may also be used to identify many other forms of online resource including data.

The intention of both systems is to provide a unique reference that may be freely shared to identify a resource such as a book, report or database. But this does not imply that full access to the document is free of charge, but this is often the case.  Several methods are reviewed here that should be accessible to small societies that seek to publish informative articles for a community of interest.

\section{Amazon Kindle Publishing Direct (KDP)}

Amazon provides a complete publication and marketing package that allows the authors sell their work online. Free publication is not possible as Amazon takes a proportion of the sales to fund the service. You can use your own ISBN or Amazon will assign one for you free of charge. Both the printed and kindle versions may be managed from the same account.

The service is easy to use for anyone with reasonable document layout skills and automated checking helps to eliminate problems as they arise. Microsoft Word templates are provided, but you are better off using specialist typesetting software if your work includes many images due to the added complexity of image management.

The finished product quality is excellent and turnaround of orders very fast.  If the publication is updated, you can choose whether to produce a new edition which is the convention for printed documents or just to update the electronic master. The latter case is normally reserved for very minor corrections.

An example published by PJP is here:

\url{https://www.amazon.co.uk/How-Build-Your-Moth-Trap/dp/1981158197}

Do be prepared for unfavourable reviews as there are people who mark the grammar and typos as a hobby.

\section{PDF with DOI}

The internet has brought many changes to academic publication and a trend towards Open Access documents that may easily be shared. Many authors publish PDF versions of their work outside the formal journal infrastructure using \enquote{pre-print} servers. The name is a little misleading since some documents may never be intended for formal publication, but their contents may help support other more substantive work.

These services are free and also suitable for publication of authoritative reports from individuals and small societies. One such service is provided by \url{https://zenodo.org}.  It is important to realise that managing changes is a feature of the service which is why it is different from posting an uncontrolled copy on a website. Other similar free services are provided by \url{https://figshare.com} and \url{https://osf.io} their common goal is the publication and sharing of research outputs. In this context, LES publication would be classed as high quality \enquote{Citizen Science} outputs. The use of DOIs would make it easier for them to be including in other research.

In the example that follows PJP has set up a community to share reports on VC55 spiders. \\
See: \url{https://zenodo.org/communities/vc55-spiders/} 

Palmer, Paul J. (2022). Report on VC55 Spider Status In The Rutland Water Area. Zenodo. \url{https://doi.org/hmrb}

This report is likely to be updated over time so the DOI \\ \url{https://doi.org/hmrb} \\will always point towards the latest version. However, each version also has its own DOI so \\
\url{https://doi.org/10.5281/zenodo.6048792} \\
 will always point towards version 1. 
 
 Note that the free service \url{http://shortdoi.org}  may be used to generate nicer looking short versions of the DOI for inclusion in reports and references. Both long and short forms are used here for illustrative purposes. This report  also includes a CSV version of the checklist as an example of how online publication may included mixed resources.

The reference can currently be found using Google, but at the time of writing seems not to be so visible on other search engines. Try the search term: \enquote{Report on VC55 Spider Status}.

\section{Producing PDF Documents}

Word processors are not really suitable for producing publication ready PDF documents as they substitute fonts and change layout rules silently. This means that the same document can look different when opened on other computers, or even when additional fonts have been loaded with other applications on a single computer. Even changing the default printer can affect the document  appearance. While many people manage to get reasonable looking results, underneath the surface are many problems with fonts and images.

Typesetting or Desktop Publishing software is more difficult to use because of the extended range of options. However, once good templates have been created that cover the options needed for a particular newsletter or report, they become much easier to use, and the quality of  output is much higher.  Typesetting software also has tools to simplify the highlighting and resolution of problems with fonts and images.

Ironically, lightweight online word processors, such as Google Docs can give excellent results as the reduced command set and centralised management gives very good consistency.

\section{PDF\textbackslash A}

The PDF\textbackslash A format has been developed for long term preservation  as it embeds all the information required to reproduce the original document, plus supporting metadata. 

Both word processors and typesetting tools have options to save as PDF\textbackslash A, but their availability may be dependent on following options relating to fonts and colour management. An excellent guide to creating PDF\textbackslash A  documents may be found here: \\ \url{https://www.research.gov/common/attachment/Desktop/How_do_I_create_a_PDF-A_file.pdf}
 
 The guide provides links to a number of free tools that may be used to convert existing Word and PDF documents into PDF\textbackslash A format. These clearly provide an easy route to the production of PDF\textbackslash A documents and presumably will warn if a document cannot be converted. 
 
 When PDF\textbackslash A documents are opened in Adobe Reader and blue banner automatically informs of the enhanced format. Try opening this document which has been saved as PDF\textbackslash A.
 
 \section{Concluding Comments}
 
Electronic publication does not supersede the role of printed media, but it does provide new routes to disseminate knowledge in a way that can be cited in other work. There are no reasons why printed reports with an ISBN should not be assigned a DOI for freely available PDF versions.

Each report produced with a DOI will be available for the foreseeable future, so it is reasonable to expect that more effort is required to ensure long term accessibility by publishing in PDF\textbackslash A format.



\bibliographystyle{unsrt}
\bibliography{references.bib}


\end{document}
